Data-Driven Search-based Software Engineering

### 2018-01-30 doc/tex/msr18/main.tex
Updates from ShareLaTeX

\begin{abstract}
This paper introduces Data-Driven Search-based Software Engineering (DSE) which combines insights from Software Analytics (SA) and Search-based Software Engineering (SBSE). SBSE reformulate the SE problem as an optimization problem and uses a meta-heuristic algorithm to solve those problems. Both the fields, SA and SBSE, are concerned with providing insights for software engineers to improve SE tasks. The similar goals of the two fields are one of the major reasons as to why these two fields should work together. 
We argue that  
combining these two fields
is useful for (a)~situations which require learning from a large data
source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

This paper also presents a  resource (tiny.cc/sbse) for exploring
Data-Driven Search-based Software Engineering.  The resource contains 89 artifacts related to data-driven search-based SE,
divided into 13 groups such as requirements engineering, software product lines, software processes, etc.
All the materials in this repository
have been   used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas

Among the numerous questions that we try to answer are: (1) What are the various topics addressed by DSE?, (2) What are the types of data used by the researchers, and, (3) What research approaches do researchers use? The paper briefly sets out to act as a practical guide to develop new data-driven techniques and also to serve as a teaching resource.
\end{abstract}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while allowing them to generate reproducible results. Also, such data can be used by
   newcomers to learn state of the art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering {all draw their case studies
from a small number of readily available defect prediction datasets} 
% \TODO{I'm not sure if it is good to say ``a small number of similar datasets''. What about saying that they all draw their case studies from open datasets?}.

@@

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}[leftmargin=*]
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

@@

{\center
\fbox{ \includegraphics[width=3in]{img/page1.png}}}
\caption{http://tiny.cc/sbse}\label{fig:one}
\end{figure}

\begin{figure*}
        \centering
        \small
        \colorbox{gray!10}{
            \begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}
                \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Problems in Search-based Software Engineering}}} \\ 
                \multicolumn{3}{c}{
                		\begin{minipage}[b]{0.33\linewidth}
                			\begin{flushleft}
                				\includegraphics[height=4.5cm]{doc/tex/msr18/img/pareto.png}
                				\vspace{8pt}
                			\end{flushleft}
                		\end{minipage}\hspace{0.1cm}
                		\begin{minipage}[b]{0.63\linewidth}
                		        \textbf{Problem: } SBSE converts a SE problem into an optimization problem, where the goal is to find the maxima or minima of objective functions {$y_i=f_i(x)$, $1 \leq i \leq m$, where  $f_i$ are the objective / evaluation functions, $m$ is the number of objectives,} x is called the \textit{independent variable}, and $y_i$ are the \textit{dependent variables}.\\
                		        \textbf{Global Maximum/Minimum: } For single objective ($m=1$) problems, algorithms aim at finding a single solution able to optimize the objective function, i.e., a global maximum/minimum. \\
                		        \textbf{Pareto Front: } For multi-objective ($m>1$) problems, there is no single `best' solution, but a number of `best' solutions. The best solutions are {non-dominated solutions} found using a \textit{dominance} relation.\\
                		        \textbf{Dominance: }The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate\\
                                another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
                                and $x_1$ is strictly better than $x_2$ in at least one objective.'' A solution is called non-dominated if no other solution dominates it.\\
                		        \textbf{Actual {Pareto Front} (PF): } A list of best solutions of a space is called Actual PF ($a\in A$). As this can be unknowable in practice or prohibitively expensive to generate, it is common to take from the union of all optimization outcomes all non-dominated solutions and use it as the (approximated) PF.\\ 
                		        \textbf{Predicted PF: } The solutions found by {an optimization} algorithm are called the Predicted PF ($p\in P$).
                		\end{minipage}
                } \\ 
                \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Components of Meta-heuristic Algorithms (search-based optimization algorithms such as NSGA-II~\cite{deb2000fast}, SPEA2~\cite{zitzler2001spea2}, MOEA/D~\cite{zhang2007moea}, AGE~\cite{wagner2015age})}}} \\
                \multicolumn{3}{c}{
                \begin{minipage}[b]{\linewidth}
                \vspace{0.1cm}
                % \TODO{I'm not sure how useful it is to explain the components here if we don't show the pseudocode of an algorithm, as the persons who don't know the components will not know the pseudocode either, and will thus be unable to understand. Perhaps we can eliminate the plot from the previous section of this figure and add a figure with a general meta-heuristic pseudocode here?}
                \begin{wrapfigure}{r}{0.4\textwidth}
                \includegraphics[height=4.8cm]{doc/tex/msr18/img/sbse_code.png}
                \end{wrapfigure}
                \textbf{Data Collection or Model building: } SBSE process can either rely on a model, which represent a software process~\cite{boehm1995cost} or can be directly applied to any software engineering problem including problems which require evaluating a solution by running a specific benchmark~\cite{krall2015gale}.

@@

                \textbf{Operators: } {These are operators that (1) generate new solutions based on one (e.g., mutation operator) or more (e.g., crossover or recombination operators) existing solutions, and (2) operators that select solutions to pass to the aforementioned operators or to survive for the next iteration of the algorithm. The operators (2) typically apply some pressure towards selecting better solutions either deterministically (e.g., elitism operator) or stochastically.} 
                % \TODO{If space allows, we can mention survival of the fittest.} % They can be used along with an}\TODO{I haven't finished this change yet. I have to come back later.} 
                \textit{elitism operator} simulates the `survival of the fittest' strategy, i.e., eliminates not so good solutions thereby preserving the good solutions in the population.

                \textbf{Generations: } {A meta-heuristic algorithm iteratively improves the population (set of solutions) iteratively. Each step of this process, which includes generation of new solutions using recombination of the existing population and selecting solutions using the elitism operator, is called a generation.  Over successive generations, the population `evolves' toward an optimal solution.}
                \end{minipage}\hspace{0.1cm}
                }
                 \\
                \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{Performance Measures (Refer to \cite{wang2016practical,chand2015manyemo} for more detail)}}} \\ 
                % \multicolumn{2}{c}{\textbf{SA}} & \textbf{SBSE} \\ \midrule
                \multicolumn{3}{c}{
                        \begin{minipage}[b]{0.33\linewidth}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/gd.png}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/igd.png}\\
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/hv.png}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/spread.png}
                                \vspace{0.5cm}
                        \end{minipage}
                        \begin{minipage}[b]{0.67\linewidth}
                            \vspace{0.1cm}
                            For single objective problems, measures such as \textit{absolute residual} or \textit{rank-difference} can be very useful and cannot be used for multi-objective problems. The following are the measures used for such problems.\\
                            \textbf{Generational Distance: } Generational distance is the measure of convergence---how close is the predicted Pareto front is to the actual Pareto front. It is defined to measure (using Euclidean distance) how far are the solutions that exist in $P$ from the nearest solutions in $A$. In an ideal case, the GD is 0, which means the predicted PF is a subset of the actual PF. Note that it ignores how well the solutions are spread out.

@@

As to defining {\em data-driven search-based SE},
we say it is some system that:
\begin{itemize}[leftmargin=*]
\item To solve  some SE problem:
\begin{itemize}
\item
It inserts  a data miner into an optimizer; or
\item
It uses an optimizer  to improve a data  miner.
\end{itemize}
\end{itemize}

@@

% A recent study by Chen et al.~\cite{xxChenSampleXXX}  illustrates the benefits
% of combining MSR+SBSE. In that study, Chen was applying SBSE 
% to many of the models in tiny.cc/sbse to 
% to optimize   decisions about software processes options, generating product lines,
% and configuring the LINUX kernel. Reviewers of that work requested that his SBSE
% results be compared to some baseline exhaustive search. According, Chen
% generated, then pruned, 10,000 random candidate solutions  using a pairwise comparison procedure.
% These results were compared with state-of-the-art
% SBSE methods that using genetic operators (combine, mutate, select, repeat)
% to carefully explore the same models.

@@

The problem with GPMs is that they do not scale beyond a dozen variables (or feaatures)~\cite{wang2016bayesian}. CART, on the other hand, is a data mining algorithm that scales efficiently
to hundreds of variables. So Nair et al. recently explored  
 active learning  for multi-objective optimization by replacing GPM with one CART tree per objective~\cite{nair2018finding}.
 The resulting system was applied to a wide range of software configuration problems
 found in tiny.cc/sbse.
 Compared to GPMs, the resulting system ran orders of magnitude faster, found solutions
 as good or better, and  scaled to much larger problems~\cite{nair2018finding}.

@@

\end{itemize} 
Note that all the above used case study material from tiny.cc/sbse.

@@

\begin{table*}[t]
\centering
\small
\caption{Different problems and associated strategies explored in this paper. The characteristic of the decision space (C/D) represents whether there are continuous or discrete in nature. The column Links represent the URL from where the problems can be download (prefix http://tiny.cc/ to the Link)---currently blinded for review.}
\label{tbl:only1}
\begin{tabular}{@{}cp{3cm}cp{0.7cm}rp{3cm}lr@{}}
\toprule
\textbf{Domain} & \textbf{Problem} & \textbf{Decision Space} & \textbf{C/D} & \textbf{Projects} & \textbf{Description} & \textbf{Links} & \textbf{Related Work} \\ \midrule
 & \cellcolor[HTML]{EFEFEF}Defect Prediction & \cellcolor[HTML]{EFEFEF}Numeric & \cellcolor[HTML]{EFEFEF}D & \cellcolor[HTML]{EFEFEF}10 & \cellcolor[HTML]{EFEFEF}CK Metric & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_data_defect}{raise\_data\_defect}} & \cellcolor[HTML]{EFEFEF}\cite{fu2016tuning} \\
 &  &  & \multicolumn{1}{c}{} & 1 &Citemap & \censor{\href{http://tiny.cc/raise_data_pits}{raise\_data\_pits}} &  \\
 &  &  & \multicolumn{1}{c}{} & 6 & Pits & \censor{\href{http://tiny.cc/raise_data_pits}{raise\_data\_pits}} &  \\
\multirow{-4}{*}{MSR} & \multirow{-3}{*}{Text Classification} & \multirow{-3}{*}{Text} & \multicolumn{1}{c}{\multirow{-3}{*}{-}} & 1 & StackOverflow & \censor{\href{http://tiny.cc/SOProcess}{SOProcess}} & \multirow{-3}{*}{\cite{agrawalwrong}} \\
 & \cellcolor[HTML]{EFEFEF}\begin{tabular}[c]{@{}l@{}}Performance\\Optimization\end{tabular} & \cellcolor[HTML]{EFEFEF}Mixed & \cellcolor[HTML]{EFEFEF}D & \cellcolor[HTML]{EFEFEF}22 & \cellcolor[HTML]{EFEFEF}Performance Configuration optimization & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_data_perf}{raise\_data\_perf}} & \cellcolor[HTML]{EFEFEF}\cite{nair2017faster, nair2017using, nair2018finding} \\
\midrule
 & Software Product Lines & Boolean & D & 5 & Product Lines & \censor{\href{http://tiny.cc/raise_data_SPL}{raise\_data\_SPL}} & \cite{chen2017sampling} \\
 & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF}7 & \cellcolor[HTML]{EFEFEF}DTLZ & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_dtlz_zdt}{raise\_dtlz\_zdt}} & \cellcolor[HTML]{EFEFEF} \\
 & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}General Optimization} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}Numeric} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}C} & \cellcolor[HTML]{EFEFEF}6 & \cellcolor[HTML]{EFEFEF}ZDT & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_dtlz_zdt}{raise\_dtlz\_zdt}} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}\cite{nair2016accidental}} \\
 & Workflow & Numeric & D & 20 & Workflow & \censor{\href{http://tiny.cc/raise_gen_workflow}{raise\_gen\_workflow}} & \cite{chen2017riot} \\
 & Text Discovery & Text & - & 4 & Reading Faster & \censor{\href{http://tiny.cc/raise_data_fastread}{raise\_data\_fastread}} & \cite{yu2016read} \\
 & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF}5 & \cellcolor[HTML]{EFEFEF}Xomo & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} \\
 & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}Software Processes} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}Numeric} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}C} & \cellcolor[HTML]{EFEFEF}4 & \cellcolor[HTML]{EFEFEF}POM3 & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_pom_xomo}{raise\_pom\_xomo}}} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}\cite{nair2016accidental, chen2017beyond}} \\
\multirow{-9}{*}{SBSE} & \begin{tabular}[c]{@{}l@{}}Requirement\\ Engineering\end{tabular} & Numeric & D & 8 & \begin{tabular}[c]{@{}l@{}}Requirement\\ Engineering\end{tabular} & \censor{\href{http://tiny.cc/raise_short}{raise\_short}} & \cite{mathew2017shorter} \\ \bottomrule
\end{tabular}
\end{table*}

@@

Accordingly, in this section, we describe sample
tasks that might be used for that exploration.
Note that:
\begin{itemize}[leftmargin=*]
\item
Table~\ref{tbl:only1} summarizes the material presented in this section. 
\item All these examples were used in recent SE
papers; i.e. for all this material, there exists baseline results against which researchers can use to  comparatively
assess  their own new ideas.
\item
Support material for that exploration (data, models, scripts),
is available from tiny.cc/sbse.

@@

\end{itemize}
Note that we make no assumption that the following list of materials
covers the spectrum of problems that could be solved by combining MSR with SBSE. In fact, one of the goals of this paper is to encourage researchers to extend this material by posting their own materials as pull requests to tiny.cc/sbse.

@@

\vspace{1.0ex}
\noindent\textbf{Challenge 1: }
Literature reviews can be extremely labor intensive and often require months (if not year) to complete. Due to a large number of papers available, the relevant papers have hard to find. A graduate student needs to review thousands of papers before finding few dozen relevant papers.
How to maximize relevant information (when there is a lot of noise) while minimizing the search cost to find relevant information?

>>>>

\begin{abstract}
This paper introduces Data-Driven Search-based Software Engineering (DSE), which combines insights from Mining Software Repositories (MSR) and Search-based Software Engineering (SBSE). While MSR formulates software engineering problems as data mining problems, SBSE reformulates SE problems as optimization problems and use meta-heuristic algorithms to solve them. Both MSR and SBSE share the common goal of providing insights to improve software engineering. The algorithms used in these two areas also have intrinsic relationships.  
We therefore argue that combining these two fields
is useful for situations (a)~which require learning from a large data
source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

This paper aims to answer the following three questions: (1) What are the various topics addressed by DSE? (2) What types of data are used by the researchers in this area? (3) What research approaches do researchers use? The paper briefly sets out to act as a practical guide to develop new DSE techniques and also to serve as a teaching resource.

This paper also presents a  resource (tiny.cc/data-se) for exploring DSE.  The resource contains 89 artifacts which are related to DSE,
divided into 13 groups such as requirements engineering, software product lines, software processes.
All the materials in this repository
have been   used in recent software engineering papers; i.e., for all this material, there exist baseline results against which researchers can comparatively assess their new ideas.

%This paper introduces Data-Driven Search-based Software Engineering (DSE) which combines insights from Mining Software Repositories (MSR) and Search-based Software Engineering (SBSE). SBSE reformulates the SE problem as an optimization problem and uses a meta-heuristic algorithm to solve those problems. Both the fields, MSR and SBSE, are concerned with providing insights for software engineers to improve SE tasks. The similar goals of the two fields are one of the major reasons why these two fields should work together. 
%We argue that  combining these two fields is useful for situations (a)~which require learning from a large data source or (b)~when optimizers need to know the lay of the land to find better solutions, faster.

%This paper also presents a  resource (tiny.cc/d-se) for exploring Data-Driven Search-based Software Engineering.  The resource contains 89 artifacts which are related to Data-driven Search-based Software Engineering, divided into 13 groups such as requirements engineering, software product lines, software processes, etc. All the materials in this repository have been   used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.

%This paper tries to answer the following three questions:: (1) What are the various topics addressed by DSE?, (2) What types of data are used by the researchers, and, (3) What research approaches do researchers use? The paper briefly sets out to act as a practical guide to develop new data-driven techniques and also to serve as a teaching resource.
\end{abstract}

@@

The MSR  community has benefited enormously from widely shared datasets.  Such datasets document the canonical problems in a field.
They serve to cluster together like-minded researchers while allowing them to generate reproducible results. Also, such data can be used by
   newcomers to learn the state of the art methods in this field. Further, they enable the mainstay of good science:
reputable, repeatable,  improvable, and even refutable results.
At the time of this writing,   nine of the 50 most cited papers in the last 5 years at IEEE Transactions of Software Engineering {all draw their case studies
from a small number of readily available defect prediction datasets.} 
% \TODO{I'm not sure if it is good to say ``a small number of similar datasets''. What about saying that they all draw their case studies from open datasets?}.

@@

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}[leftmargin=*]
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/data-se,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

@@

{\center
\fbox{ \includegraphics[width=3in]{img/page1.png}}}
\caption{http://tiny.cc/data-se}\label{fig:one}
\end{figure}

\begin{figure*}
        \centering
        \small
        \colorbox{gray!10}{
            \begin{tabular}{@{}p{3cm}p{6cm}p{8.35cm}@{}}
                \multicolumn{3}{c}{\cellcolor{gray}\textcolor{white}{\textbf{Problems in Search-based Software Engineering}}} \\ 
                \multicolumn{3}{c}{
                		\begin{minipage}[b]{0.33\linewidth}
                			\begin{flushleft}
                				\includegraphics[height=4.5cm]{doc/tex/msr18/img/pareto.png}
                				\vspace{8pt}
                			\end{flushleft}
                		\end{minipage}\hspace{0.1cm}
                		\begin{minipage}[b]{0.63\linewidth}
                		        \textbf{Problem: } SBSE converts a SE problem into an optimization problem, where the goal is to find the maxima or minima of objective functions {$y_i=f_i(x)$, $1 \leq i \leq m$, where  $f_i$ are the objective / evaluation functions, $m$ is the number of objectives,} x is called the \textit{independent variable}, and $y_i$ are the \textit{dependent variables}.\\
                		        \textbf{Global Maximum/Minimum: } For single objective ($m=1$) problems, algorithms aim at finding a single solution able to optimize the objective function, i.e., a global maximum/minimum. \\
                		        \textbf{Pareto Front: } For multi-objective ($m>1$) problems, there is no single `best' solution, but a number of `best' solutions. The best solutions are {non-dominated solutions} found using a \textit{dominance} relation.\\
                		        \textbf{Dominance: }The domination criterion  can be defined as: ``A solution $x_1$ is said to dominate\\
                                another solution $x_2$, if $x_1$ is no worse than $x_2$ in all objectives
                                and $x_1$ is strictly better than $x_2$ in at least one objective.'' A solution is called non-dominated if no other solution dominates it.\\
                		        \textbf{Actual {Pareto Front} (PF): } A list of best solutions of a space is called Actual PF ($a\in A$). As this can be unknowable in practice or prohibitively expensive to generate, it is common to take from the union of all optimization outcomes all non-dominated solutions and use it as the (approximated) PF.\\ 
                		        \textbf{Predicted PF: } The solutions found by {an optimization} algorithm are called the Predicted PF ($p\in P$).
                		\end{minipage}
                } \\ 
                \multicolumn{3}{c}{\cellcolor{gray}\textcolor{white}{\textbf{Components of Meta-heuristic Algorithms (search-based optimization algorithms such as NSGA-II~\cite{deb2000fast}, SPEA2~\cite{zitzler2001spea2}, MOEA/D~\cite{zhang2007moea}, AGE~\cite{wagner2015age})}}} \\
                \multicolumn{3}{c}{
                \begin{minipage}[b]{\linewidth}
                \vspace{0.1cm}
                % \TODO{I'm not sure how useful it is to explain the components here if we don't show the pseudocode of an algorithm, as the persons who don't know the components will not know the pseudocode either, and will thus be unable to understand. Perhaps we can eliminate the plot from the previous section of this figure and add a figure with a general meta-heuristic pseudocode here?}
                \begin{wrapfigure}{r}{0.4\textwidth}
                \includegraphics[height=4.8cm]{doc/tex/msr18/img/sbse_code.png}
                \end{wrapfigure}
                \textbf{Data Collection or Model building: } SBSE process can either rely on a model, which represent a software process~\cite{boehm1995cost} or can be directly applied to any software engineering problem including problems which require evaluating a solution by running a specific benchmark~\cite{krall2015gale}.

@@

                \textbf{Operators: } {These are operators that (1) generate new solutions based on one (e.g., mutation operator) or more (e.g., crossover or recombination operators) existing solutions, and (2) operators that select solutions to pass to the aforementioned operators or to survive for the next iteration of the algorithm. The operators (2) typically apply some pressure towards selecting better solutions either deterministically (e.g., elitism operator) or stochastically.} 
                % \TODO{If space allows, we can mention survival of the fittest.} % They can be used along with an}\TODO{I haven't finished this change yet. I have to come back later.} 
                \textit{Elitism operator} simulates the `survival of the fittest' strategy, i.e., eliminates not so good solutions thereby preserving the good solutions in the population.

                \textbf{Generations: } {A meta-heuristic algorithm iteratively improves the population (set of solutions) iteratively. Each step of this process, which includes generation of new solutions using recombination of the existing population and selecting solutions using the elitism operator, is called a generation.  Over successive generations, the population `evolves' toward an optimal solution.}
                \end{minipage}\hspace{0.1cm}
                }
                 \\
                \multicolumn{3}{c}{\cellcolor{gray}\textcolor{white}{\textbf{Performance Measures (Refer to \cite{wang2016practical,chand2015manyemo} for more detail)}}} \\ 
                % \multicolumn{2}{c}{\textbf{SA}} & \textbf{SBSE} \\ \midrule
                \multicolumn{3}{c}{
                        \begin{minipage}[b]{0.33\linewidth}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/gd.png}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/igd.png}\\
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/hv.png}
                                \includegraphics[height=2.8cm]{doc/tex/msr18/img/spread.png}
                                \vspace{0.5cm}
                        \end{minipage}
                        \begin{minipage}[b]{0.67\linewidth}
                            \vspace{0.1cm}
                            For single objective problems, measures such as \textit{absolute residual} or \textit{rank-difference} can be very useful and cannot be used for multi-objective problems. The following are the measures used for such problems.\\
                            \textbf{Generational Distance: } Generational distance is the measure of convergence---how close is the predicted Pareto front is to the actual Pareto front. It is defined to measure (using Euclidean distance) how far are the solutions that exist in $P$ from the nearest solutions in $A$. In an ideal case, the GD is 0, which means the predicted PF is a subset of the actual PF. Note that it ignores how well the solutions are spread out.

@@

As to defining {\em data-driven search-based SE},
we say it is some system that:
\begin{itemize}[leftmargin=*]
\item To solve  an SE problem:
\begin{itemize}
\item
It inserts  a data miner into an optimizer; or
\item
It uses an optimizer  to improve a data  miner.
\end{itemize}
\end{itemize}

@@

% A recent study by Chen et al.~\cite{xxChenSampleXXX}  illustrates the benefits
% of combining MSR+SBSE. In that study, Chen was applying SBSE 
% to many of the models in tiny.cc/d-se to 
% to optimize   decisions about software processes options, generating product lines,
% and configuring the LINUX kernel. Reviewers of that work requested that his SBSE
% results be compared to some baseline exhaustive search. According, Chen
% generated, then pruned, 10,000 random candidate solutions  using a pairwise comparison procedure.
% These results were compared with state-of-the-art
% SBSE methods that using genetic operators (combine, mutate, select, repeat)
% to carefully explore the same models.

@@

The problem with GPMs is that they do not scale beyond a dozen variables (or features)~\cite{wang2016bayesian}. CART, on the other hand, is a data mining algorithm that scales efficiently
to hundreds of variables. So Nair et al. recently explored  
 active learning  for multi-objective optimization by replacing GPM with one CART tree per objective~\cite{nair2018finding}.
 The resulting system was applied to a wide range of software configuration problems
 found in tiny.cc/data-se.
 Compared to GPMs, the resulting system ran orders of magnitude faster, found solutions
 as good or better, and  scaled to much larger problems~\cite{nair2018finding}.

@@

\end{itemize} 
Note that all the above used case study material from tiny.cc/data-se.

@@

\begin{table*}[t]
\centering
\small
\caption{Different problems and associated strategies explored in this paper. The characteristic of the decision space (C/D) represents whether there are continuous or discrete in nature. The column Links represent the URL from where the problems can be download (prefix http://tiny.cc/ to the Link)---currently blinded for review.}
\label{tbl:only1}
\begin{tabular}{@{}cp{3cm}cp{0.7cm}rp{3cm}lr@{}}
\toprule
\textbf{Domain} & \textbf{Problem} & \textbf{Decision Space} & \textbf{C/D} & \textbf{Projects} & \textbf{Description} & \textbf{Links} & \textbf{Related Work} \\ \midrule
 & \cellcolor[HTML]{EFEFEF}Defect Prediction & \cellcolor[HTML]{EFEFEF}Numeric & \cellcolor[HTML]{EFEFEF}D & \cellcolor[HTML]{EFEFEF}10 & \cellcolor[HTML]{EFEFEF}CK Metric & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_data_defect}{raise\_data\_defect}} & \cellcolor[HTML]{EFEFEF}\cite{fu2016tuning} \\
 &  &  & \multicolumn{1}{c}{} & 1 &Citemap & \censor{\href{http://tiny.cc/raise_data_pits}{raise\_data\_pits}} &  \\
 &  &  & \multicolumn{1}{c}{} & 6 & Pits & \censor{\href{http://tiny.cc/raise_data_pits}{raise\_data\_pits}} &  \\
\multirow{-4}{*}{MSR} & \multirow{-3}{*}{Text Classification} & \multirow{-3}{*}{Text} & \multicolumn{1}{c}{\multirow{-3}{*}{-}} & 1 & StackOverflow & \censor{\href{http://tiny.cc/SOProcess}{SOProcess}} & \multirow{-3}{*}{\cite{agrawalwrong}} \\
 & \cellcolor[HTML]{EFEFEF}\begin{tabular}[c]{@{}l@{}}Performance\\Optimization\end{tabular} & \cellcolor[HTML]{EFEFEF}Mixed & \cellcolor[HTML]{EFEFEF}D & \cellcolor[HTML]{EFEFEF}22 & \cellcolor[HTML]{EFEFEF}Performance Configuration optimization & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_data_perf}{raise\_data\_perf}} & \cellcolor[HTML]{EFEFEF}\cite{nair2017faster, nair2017using, nair2018finding} \\
\midrule
 & Software Product Lines & Boolean & D & 5 & Product Lines & \censor{\href{http://tiny.cc/raise_data_SPL}{raise\_data\_SPL}} & \cite{chen2017sampling} \\
 & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF} & \cellcolor[HTML]{EFEFEF}7 & \cellcolor[HTML]{EFEFEF}DTLZ & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_dtlz_zdt}{raise\_dtlz\_zdt}} & \cellcolor[HTML]{EFEFEF} \\
 & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}General Optimization} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}Numeric} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}C} & \cellcolor[HTML]{EFEFEF}6 & \cellcolor[HTML]{EFEFEF}ZDT & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_dtlz_zdt}{raise\_dtlz\_zdt}} & \multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}\cite{nair2016accidental}} \\
 & Workflow & Numeric & D & 20 & Workflow & \censor{\href{http://tiny.cc/raise_gen_workflow}{raise\_gen\_workflow}} & \cite{chen2017riot} \\
 & \cellcolor[HTML]{EFEFEF}Text Discovery &\cellcolor[HTML]{EFEFEF} Text & \cellcolor[HTML]{EFEFEF}- & \cellcolor[HTML]{EFEFEF}4 & \cellcolor[HTML]{EFEFEF}Reading Faster & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_data_fastread}{raise\_data\_fastread}} & \cellcolor[HTML]{EFEFEF}\cite{yu2016read} \\
 &  &  &  & 5 & Xomo &  &  \\
 & \multirow{-2}{*}{Software Processes} & \multirow{-2}{*}{Numeric} & \multirow{-2}{*}{C} & 4 & POM3 & \multirow{-2}{*}{\censor{\href{http://tiny.cc/raise_pom_xomo}{raise\_pom\_xomo}}} & \multirow{-2}{*}{\cite{nair2016accidental, chen2017beyond}} \\
\multirow{-9}{*}{SBSE} & \cellcolor[HTML]{EFEFEF}{\begin{tabular}[c]{@{}l@{}}Requirement\\ Engineering\end{tabular}} & \cellcolor[HTML]{EFEFEF}Numeric & \cellcolor[HTML]{EFEFEF}D & \cellcolor[HTML]{EFEFEF}8 &
\cellcolor[HTML]{EFEFEF}{\begin{tabular}[c]{@{}l@{}}Requirement\\ Engineering\end{tabular}} & \cellcolor[HTML]{EFEFEF}\censor{\href{http://tiny.cc/raise_short}{raise\_short}} & \cellcolor[HTML]{EFEFEF}\cite{mathew2017shorter} \\ \bottomrule
\end{tabular}
\end{table*}

@@

Accordingly, in this section, we describe sample
tasks that might be used for that exploration.
Note that:
\begin{itemize}[leftmargin=*]
\item
Table~\ref{tbl:only1} summarizes the material presented in this section. 
\item All these examples were used in recent SE
papers; i.e. for all this material, there exists baseline results against which researchers can use to  comparatively
assess  their own new ideas.
\item
Support material for that exploration (data, models, scripts),
is available from tiny.cc/data-se.

@@

\end{itemize}
Note that we make no assumption that the following list of materials
covers the spectrum of problems that could be solved by combining MSR with SBSE. In fact, one of the goals of this paper is to encourage researchers to extend this material by posting their own materials as pull requests to tiny.cc/data-se.

@@

\vspace{1.0ex}
\noindent\textbf{Challenge 1: }
Literature reviews can be extremely labor intensive and often require months (if not year) to complete. Due to the large number of papers available, the relevant papers are hard to find. A graduate student needs to review thousands of papers before finding the few dozen relevant ones.
Therefore the challenge is: how to maximize relevant information (when there is a lot of noise) while minimizing the search cost to find relevant information?
